---
title: "EDA-LA1"
output: html_document
date: "`r Sys.Date()`"
---

### 1. Search command: Gives a list of packages loaded
```{r}
search()
```

### 2. Loading the data set
```{r}
dataset <- read.csv("UP-Crime-Data-Year-2019.csv")
```

### 3. List command
```{r}
ls()
```

### Details of the data set

#### 4. Summary of the data set
```{r}
summary(dataset)
```

#### 5. Head

```{r}
head(dataset)
```

#### 6. Tail
```{r}
tail(dataset)
```

#### 7. Head of first 5
```{r}
head(dataset,5)
```

#### 8. Tail of 5
```{r}
tail(dataset,5)
```

#### 9. Structure of data set
```{r}
str(dataset)
```

#### 10. Get the names of the object
```{r}
names(dataset)
```

#### 11. Names of the columns
```{r}
colnames(dataset)
```

#### 12. Names of the rows
```{r}
rownames(dataset)
```

#### 13. Class of the dataset
```{r}
class(dataset)
```

### 14. Set of the dataset
```{r}
x <- data.frame(dataset$City, dataset$Number.of.adult.victims)

x
```

### 15. Sum of NA values
```{r}
colSums(is.na(dataset))
```

### 16. Maximum of number of adult victims with NA values
```{r}
max(dataset$Number.of.male.victims.adult.)
```

### 17. Maximum of number of adult victims
```{r}
max(dataset$Number.of.male.victims.adult.,na.rm = TRUE)
```

### 18. Minimum of number of adult victims with NA values
```{r}
min(dataset$Number.of.male.victims.adult.)
```

### 19. Minimum of number of adult victims
```{r}
min(dataset$Number.of.male.victims.adult.,na.rm = TRUE)
```

### 20. Median of number of adult victims with NA values
```{r}
median(dataset$Number.of.male.victims.adult.)
```

### 21. Median of number of adult victims
```{r}
median(dataset$Number.of.male.victims.adult.,na.rm = TRUE)
```

### 22. Mode of number of adult victims with NA values
```{r}
mode(dataset$Number.of.male.victims.adult.)
```

### 23. Mode of number of adult victims
```{r}
mode(dataset$Number.of.male.victims.adult.)
```

### 24. Standard deviation of number of adult victims with NA values
```{r}
sd(dataset$Number.of.male.victims.adult.)
```

### 25. Mode of number of adult victims
```{r}
sd(dataset$Number.of.male.victims.adult.,na.rm = TRUE)
```

### 26. Sorted Number of male victims
```{r}
sort(dataset$Number.of.male.victims.adult.)
```

### 27. Sorted first row
```{r}
sort(dataset[1,])
```

### 28. Order
```{r}
order(dataset$Number.of.child.victims,na.last = TRUE)
```

### 29. Rank
```{r}
rank(dataset$Number.of.child.victims,na.last = TRUE)
```

### 30. Dimension names to look at the rows and columns at the same time
```{r}
dimnames(dataset)
```
