---
title: "EDA-LA1"
output: html_document
date: "`r Sys.Date()`"
---

Submitted By-
Aditya Nair (1NT19IS006)
Amaan Mohib (1NT19IS012)

### [GitHub Repo](https://github.com/amaan-mohib/eda-la1)

### 1. Search command: Gives a list of packages loaded
```{r}
search()
```

### 2. Loading the data set
```{r}
dataset <- read.csv("UP-Crime-Data-Year-2019.csv")
```

### 3. List command
```{r}
ls()
```

### Details of the data set

#### 4. Summary of the data set
```{r}
summary(dataset)
```

#### 5. Head

```{r}
head(dataset)
```

#### 6. Tail
```{r}
tail(dataset)
```

#### 7. Head of first 5
```{r}
head(dataset,5)
```

#### 8. Tail of 5
```{r}
tail(dataset,5)
```

#### 9. Structure of data set
```{r}
str(dataset)
```

#### 10. Get the names of the object
```{r}
names(dataset)
```

#### 11. Names of the columns
```{r}
colnames(dataset)
```

#### 12. Names of the rows
```{r}
rownames(dataset)
```

#### 13. Class of the dataset
```{r}
class(dataset)
```

### 14. Set of the dataset
```{r}
x <- data.frame(dataset$City, dataset$Number.of.adult.victims)

x
```

### 15. Sum of NA values
```{r}
colSums(is.na(dataset))
```

### 16. Maximum of number of adult victims with NA values
```{r}
max(dataset$Number.of.male.victims.adult.)
```

### 17. Maximum of number of adult victims
```{r}
max(dataset$Number.of.male.victims.adult.,na.rm = TRUE)
```

### 18. Minimum of number of adult victims with NA values
```{r}
min(dataset$Number.of.male.victims.adult.)
```

### 19. Minimum of number of adult victims
```{r}
min(dataset$Number.of.male.victims.adult.,na.rm = TRUE)
```

### 20. Median of number of adult victims with NA values
```{r}
median(dataset$Number.of.male.victims.adult.)
```

### 21. Median of number of adult victims
```{r}
median(dataset$Number.of.male.victims.adult.,na.rm = TRUE)
```

### 22. Mode of number of adult victims with NA values
```{r}
mode(dataset$Number.of.male.victims.adult.)
```

### 23. Mode of number of adult victims
```{r}
mode(dataset$Number.of.male.victims.adult.)
```

### 24. Standard deviation of number of adult victims with NA values
```{r}
sd(dataset$Number.of.male.victims.adult.)
```

### 25. Mode of number of adult victims
```{r}
sd(dataset$Number.of.male.victims.adult.,na.rm = TRUE)
```

### 26. Sorted Number of male victims
```{r}
sort(dataset$Number.of.male.victims.adult.)
```

### 27. Sorted first row
```{r}
sort(dataset[1,])
```

### 28. Order
```{r}
order(dataset$Number.of.child.victims,na.last = TRUE)
```

### 29. Rank
```{r}
rank(dataset$Number.of.child.victims,na.last = TRUE)
```

### 30. Dimension names to look at the rows and columns at the same time
```{r}
dimnames(dataset)
```
###31.

```{r}
predictor=c(rep('open',5),rep('closed',4))
```
### 32.
```{r}
length(dataset$Number.of.male.victims.adult.)
```
### 33
```{r}
xyz=with(dataset,order(dataset$City,dataset$Title))

xyz
```
### 34
```{r}
dataset.mat=as.matrix(dataset)

dataset.mat
```
### 35 -converted from data frame to list
```{r}
frame.list=as.list(dataset)

frame.list
```
###36 Standard Deviation 
```{r}
sd(dataset$City)
```
### 37 Standard Deviation w/o na
```{r}
sd(dataset$City,na.rm = TRUE)
```
### 38 na.omit - used to strip out NA items
```{r}
length(na.omit(dataset$City))
```
### 39 - Gives Log 
```{r}
log(dataset$Number.of.male.victims.adult.)
```
### 40 Rotates Data Frame
```{r}
t(dataset)
```
### 41
```{r}
# rowMeans(dataset$Number.of.male.victims.adult.,dims=1)
```
### 42
```{r}
margin.table(array(dataset$Number.of.child.victims))
```
### 43
```{r}
prop.table(dataset$Kidnnaping..Number.of.child.victims)
```
### 44. Initializing libraries
```{r}
library(gcookbook)
```
```{r}
library(dplyr)
```
```{r}
installed.packages()
```
### 45. Rename
```{r}
dataset %>% rename(Reason=Murder.Happened.with.reason..1.Property.Land.Disputes..2.Family.Dispute.3.Petty.Quarrels..4.Money.Disputes...5.Personal.Vendetta...6.Love.Affairs...7.Casteism.8..Unknown.other)
```
### 46. 
```{r}
prop.table(dataset$Number.of.female.victims.adult.)
```
### 47.
```{r}
dataset %>% rename(Reason=Murder.Happened.with.reason..1.Property.Land.Disputes..2.Family.Dispute.3.Petty.Quarrels..4.Money.Disputes...5.Personal.Vendetta...6.Love.Affairs...7.Casteism.8..Unknown.other, Act=Crime.Against.Women...Combined....1..Murder.with.Rape..2..Dowry.Deaths.Sec..3048..3..Suicide.sec.305.306..4..Kidnapping.All..5..Acid.Attack.Sec..326A.IPC..6..Cruelty.by.Husband.in.laws..Sec.498.A.IPC..7..Rape.only.Sec..376.or.511.IPC..8..Assault.on.Women.with.Intent.to.Outrage.her.Modesty..Sec..354.IPC..9..Cyber.Crimes.against.Women.10..Protection.of.Children.from.Sexual.Offences.Act)
```
### 48. New column
```{r}
dataset %>% mutate(newcol=NA)
```
### 49
```{r}
dataset %>% mutate(newcol=NA,ncol=6)
```
### 50
```{r}
dataset %>% filter(City=="Lucknow")
```
### 51
```{r}
dataset %>% filter(City=="Kanpur" & Number.of.child.victims>1 & Number.of.female.victims.adult.>1)
```
### 52. Creating tables
```{r}
table(dataset$City)
```
### 53. 
```{r}
table(dataset$Number.of.male.victims.adult.)
```
### 54
```{r}
t.test(dataset$Number.of.child.victims,dataset$Number.of.male.victims.adult.)
```
### 55
```{r}
cor(dataset$Number.of.child.victims,dataset$Number.of.male.victims.adult.)
```
### 56
```{r}
t.test(dataset$Number.of.adult.victims,dataset$Number.of.male.victims.adult.,paired = TRUE)
```
### 57
```{r}
IQR(dataset$Number.of.male.victims.adult.,na.rm=TRUE)
```
### 58
```{r}
sapply(dataset, class)
```
### 59
```{r}
hist(dataset$Number.of.male.victims.adult.)
```
### 60
```{r}
boxplot(dataset$Number.of.child.victims)
```
### 61
```{r}
hist(dataset$Kidnnaping..Number.of.child.victims)
```
### 62
```{r}
boxplot(dataset$Number.of.female.victims.adult.)
```
### 63
```{r}
stem(dataset$Number.of.child.victims)
```
### 64
```{r}
#plot(dataset$Number.of.child.victims-dataset$Kidnnaping..Number.of.child.victims)
```
```{r}
cat("Hello world")
```

```{r}
seq(5)
```
```{r}
seq(2, 5, 0.5)
```
```{r}
seq(2,5, length.out = 10)
```
```{r}
rep(1:5, 2)
```
  
```{r}
rep(1:5, c(1,1,1,2,2))
```
```{r}
Sys.Date()
```

```{r}
Sys.time()
```

```{r}
x <- 12.3
y <- 12L
typeof(x)
typeof(y)
```

```{r}
subset(dataset, select = c("City", "Title"))
```
```{r}
P <- c(rep('A' , 3) , rep('B' , 10) , rep('C' , 7) )
t <- table(P) 
pie(t)
```
```{r}
plot(x = cars$speed, y = cars$dist, pch = 1, col = 1,
 main = "Distance vs Speed of Cars",
 xlab = "Speed", ylab = "Distance")
```

```{r}
with(cars, plot(dist~speed, pch = 2, col = 3,
 main = "Distance to stop vs Speed of Cars",
 xlab = "Speed", ylab = "Distance"))
```

```{r}
help()
```

```{r}
getwd
```

```{r}
dir()
```
```{r}
log(x)
```

```{r}
rm(x)
```

```{r}
ceiling(1.6) 
```
```{r}
floor(1.8)
```

```{r}
round(1.2345,2)
```