---
title: "EDA la-2"
date: '2022-07-03'
output: html_document
---

Submitted By-
Aditya Nair (1NT19IS006) 
Amaan Mohib (1NT19IS012)

### [GitHub Repo](https://github.com/amaan-mohib/eda-la1)

###  Loading the data set
```{r}
dataset <- read.csv("UP-Crime-Data-Year-2019.csv")
```

# creating a scatter plot
```{r}
library(ggplot2)

ggplot(dataset, aes(x = City, y = dataset$Number.of.male.victims.adult.)) +
 geom_point()

```

# creating a line graph
```{r}
ggplot(dataset, aes(x = City, y = dataset$Number.of.male.victims.adult.)) +
 geom_line()
```

# Creating a Bar Graph
```{r}
ggplot(dataset, aes(x = dataset$City, y = dataset$Number.of.male.victims.adult.)) +
 geom_col()
```

# creating a histogram
```{r}
ggplot(dataset, aes( x = Number.of.male.victims.adult.)) +
  geom_histogram(binwidth = 4)
```

# creating a box plot
```{r}
ggplot(dataset, aes(x = dataset$City, y = dataset$Number.of.male.victims.adult.)) +
  geom_boxplot()
```

# grouping graph together
```{r}
ggplot(dataset, aes(x = dataset$City, y = dataset$Number.of.male.victims.adult., fill = City)) +
 geom_col(position = "dodge")
```

# making bargraph of counts
```{r}
ggplot(dataset, aes(x = dataset$Number.of.male.victims.adult.)) +
 geom_bar()
```

# adjusting a bar width and space
```{r}
ggplot(dataset, aes(x = dataset$City, y = dataset$Number.of.male.victims.adult.)) +
 geom_col(width = 0.5)
```
# stacked bar graph
```{r}
ggplot(dataset, aes(x = dataset$City, y = dataset$Number.of.male.victims.adult.)) +
 geom_col()
```

# Cleveland Dot plot
```{r}
ggplot(dataset, aes(y = dataset$City, x = dataset$Number.of.male.victims.adult.)) +
 geom_point()
```

# Line graph
```{r}
ggplot(dataset, aes(y = dataset$City, x = dataset$Number.of.male.victims.adult.)) +
 geom_line()
```

# Line graph with points
```{r}
ggplot(dataset, aes(y = dataset$City, x = dataset$Number.of.male.victims.adult.)) +
 geom_line() +
  geom_point()
```

# Line graph with colour
```{r}
ggplot(dataset, aes(y = dataset$City, x = dataset$Number.of.male.victims.adult.)) +
 geom_line(linetype = "dashed", size = 1, colour = "blue")
```

# graph with shaded area
```{r}
ggplot(dataset, aes(y = dataset$City, x = dataset$Number.of.male.victims.adult.)) +
 geom_area()
```

# Making histogram
```{r}
ggplot(dataset, aes(x = dataset$Number.of.male.victims.adult.)) +
 geom_histogram()
```

# Making histogram with facet
```{r}
ggplot(dataset, aes(x = dataset$Number.of.male.victims.adult.)) +
 geom_histogram() +
  facet_grid(City ~ .)
```

# Making density curve
```{r}
ggplot(dataset, aes(x = dataset$Number.of.male.victims.adult.)) +
 geom_density()
```

# Making frequency plygon
```{r}
ggplot(dataset, aes(x = dataset$Number.of.male.victims.adult.)) +
 geom_freqpoly()
```

# creating a violin plot
```{r}
ggplot(dataset, aes(x = dataset$City, y = dataset$Number.of.male.victims.adult.)) +
  geom_violin()
```

# creating a violin plot with box plot
```{r}
ggplot(dataset, aes(x = dataset$City, y = dataset$Number.of.male.victims.adult.)) +
  geom_violin() +
  geom_boxplot(width = .1, fill = "black", outlier.colour = NA)
```

# creating a violin plot with smoothing
```{r}
ggplot(dataset, aes(x = dataset$City, y = dataset$Number.of.male.victims.adult.)) +
  geom_violin(adjust=2)
```
```{r}
ggplot(dataset, aes(x = dataset$City, y = dataset$Number.of.male.victims.adult.)) +
  geom_violin(adjust=.5)
```

# Making a dotplot
```{r}
ggplot(dataset, aes(x = dataset$Number.of.male.victims.adult.)) +
 geom_dotplot()
```

# Making a dotplot with boxplot
```{r}
ggplot(dataset, aes(x = dataset$Number.of.male.victims.adult.)) +
  geom_boxplot(outlier.colour = NA, width = .4) +
 geom_dotplot()
```

Note: Some of commands were not working for our dataset